---
title: "combining and describing exit ticket surveys"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

# Loading and setting up

```{r}
library(tidyverse)
library(here)
library(janitor)
```

# Reading data

```{r}
#eoc1 <- read_csv(here::here("data", "eoc-1.csv"))
#eoc3 <- read_csv(here::here("data", "eoc-3.csv"))
#eoc4 <- read_csv(here::here("data", "eoc-4.csv"))
#eoc5 <- read_csv(here::here("data", "eoc-5.csv"))
#pre <- read.csv(here::here("data", "pre-survey.csv"))
#post <- read.csv(here::here("data", "post-survey.csv"))
combo <- read_csv(here::here("data", "eoc_combo.csv"))
comment <- read_csv(here::here("data", "combo_organize_notes.csv"))
ordered <- read_csv(here::here("data", "Survey_date.csv"))
  
```

# Filtering responses
## The following code is to focus the number of columns that we need to use when we are analyzing the data. 
### - Start date = when the individual started the intial survey.
### - EndDate = when the individual finished the survey. 
### - Progress = how much of the survey was completed. 
#### Most individuals completed the surveys to the 100 percent level
### - RecipientEmail = the individuals email
### - ResponseID = the ID that was creatd by the system 
### - Survey = which of the 5 surveys the response was associated. 
### Q1_1 , Q1_2, Q1_3, Q1_4, Q2 = the questions that were asked on each of the surveys given to the participants. 
```{r}
selected <- combo %>% 
  select(StartDate,EndDate,Progress,RecipientEmail, ResponseId, Survey, Q1_1, Q1_2, Q1_3, Q1_4, Q2)%>%
  arrange(StartDate)%>%
write_csv("combo_organize.csv")
```
##The following code separates individual questions from all other questions in the surveys. Then each separated question is designated by the survey it was pulled from (EOC 1-5). 


```{r}
comment %>%
  select(Survey,Q1_1)%>%
  count()


comment %>%
  select(Survey,Q1_2)%>%
  count()


comment %>%
  select(Survey,Q1_3)%>%
  count()


comment %>%
  select(Survey,Q1_4)%>%
  count()


comment %>%
  select(Survey, Q2)%>%
  count()


comment %>%
  select(Survey, Q2_code)%>%
  count()
```

## Some of the participants used the same link on multiple days that could alter the analysis of the data. This code will divide when each of the survey responses were sent (the EndDate) to researchers. 

```{r}
comment %>%
  select(Survey, EndDate)%>%
  count()
  
  
```

##Breakdown Question by time points
### Theses coded are further investigation of when each of the questions were sent. This will assist in the separation by date to ensure responses are truly chronological when they participated in the events of the study. 


```{r}
comment %>%
  janitor::tabyl(EndDate, Q1_1)
```

```{r}
comment %>%
  janitor::tabyl(EndDate, Q1_2)
```

```{r}
comment %>%
  janitor::tabyl(EndDate, Q1_3)
```

```{r}
comment %>%
  janitor::tabyl(EndDate, Q1_4)
```


```{r}
comment %>%
  janitor::tabyl(EndDate, Q2_code)
```
